---
title: "HW_8"
author: "Emily Wygal"
date: "2025-04-10"
output: pdf_document
---

Name: Emily Wygal UT EID: eew2267 Github link: <https://github.com/EmElWy/Homework_8>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#necessary packages
library(ggplot2)
library(tidyverse)
library(mosaic)
```

## Homework 8

### **Problem 1**

```{r, echo=FALSE, results='hide'}
creatinine <- read.csv("creatinine.csv")

model_creat = lm(creatclear ~ age, data=creatinine)
coef(model_creat)

age55 = -0.6198159*(55) + 147.8129158
age55

age40 = -0.6198159*(40) + 147.8129158
age40
135 - age40


age60 = -0.6198159*(60) + 147.8129158
age60
112 - age60

```
##### Part A: 

Using the data of creatinine clearance rate and age, I calculated a linear regression model equation: y = -0.6198159x + 147.8129158. After Plugging in 55 for x, we should expect a 55 year old to have a creatinine clearance rate of 113.723 ml/minute. 


##### Part B: 

Looking at the equation we generated (y = -0.6198159x + 147.8129158), the -0.6198159 is the creatinine clearance rate change with age. Moreover, this means that for each year someone increases in age, the creatinine clearance decreases by approximately 0.62 ml/min.


##### Part C: 

I first found the expected creatinine clearance rate for the 40 year old by plugging in x = 40, and I got 123.0203. Then I found the difference between the actual and predicted value: 11.9797. Then I the expected creatinine clearance rate by plugging in x = 60, and I got 110.624; I calculated the difference between the actual and predicted value and got 1.3760.


### **Problem 2**


##### Part 1:

We estimated a growth rate of 18.3% for Italy, and a doubling time of 3.8 days. I calculated a 95% bootstrapped confidence interval for the growth rate of 0.159 to 0.208. I calculated a 95% bootstrapped confidence interval for the doubling time of 3.4 to 4.4 days.

```{r, echo=FALSE, results='hide'}

covid <- read.csv("covid.csv")
italy <- covid %>% filter(country == "Italy")

# Fit exponential growth model for Italy
model_italy <- lm(log(deaths) ~ days_since_first_death, data = italy)

#find equation/slope
round(coef(model_italy)[2], 3)
italy_rate <- 100*0.183

#doubling time
italy_double <- round(70 / italy_rate, 1)


italy_boot <- do(10000)*round((coef(lm(log(deaths) ~ days_since_first_death, data = resample(italy)))[2]), 3)
double_iboot <- do(10000)*round((70 / (100*coef(lm(log(deaths) ~ days_since_first_death, data = resample(italy)))[2])), 1)

confint(italy_boot, level = 0.95)
confint(double_iboot, level = 0.95)

```


##### Part 2:

We estimated a growth rate of 27.6% for Italy, and a doubling time of 2.5 days. I calculated a 95% bootstrapped confidence interval for the growth rate of 0.235 to 0.318. I calculated a 95% bootstrapped confidence interval for the doubling time of 2.2 to 3 days.


```{r, echo=FALSE, results='hide'}
spain <- covid %>% filter(country == "Spain")

# Fit exponential growth model for Spain
spain_model <- lm(log(deaths) ~ days_since_first_death, data = spain)

# Fit exponential growth model for Italy
model_spain <- lm(log(deaths) ~ days_since_first_death, data = spain)

#find equation/slope
round(coef(model_spain)[2], 3)
spain_rate <- 100*0.276

#doubling time
spain_double <- round(70 / spain_rate, 1)

spain_boot <- do(10000)*round((coef(lm(log(deaths) ~ days_since_first_death, data = resample(spain)))[2]), 3)
double_sboot <- do(10000)*round((70 / (100*coef(lm(log(deaths) ~ days_since_first_death, data = resample(spain)))[2])), 1)

confint(spain_boot, level = 0.95)
confint(double_sboot, level = 0.95)

```


##### Part 3:


```{r, echo = FALSE}

covid_ggplot <-  ggplot(covid)

covid_ggplot + geom_line(aes(x=days_since_first_death, y=deaths, color = country)) + labs(title = "Reported Daily COVID-19 Deaths in Italy and Spain", x = "Days Since First Death", y = "Reported Deaths")

```



### **Problem 3**

To estimate the elasticity, I used the formula Q = KP^Beta, and applied the log function, to get log(Q) = log(K) + Beta*log(P). Then I applied this to the milk data, generating a linear regression model for the log of the price and log of the sales. The slope of this regression line would be my beta estimate: I estimate price elasticity of demand for milk is -1.62. I calculated a 95% bootstrapped confidence interval for the price elasticity of -1.774 to -1.459	.
 
```{r, echo=FALSE, results='hide'}

milk <- read.csv("milk.csv")

# estimate linear(log - log) model
milk_model <- lm(log(sales) ~ log(price), data = milk)
#find beta estimate ( log(Q) = log(K) + Beta*log(P) )
coef(milk_model)[2]
beta = -1.62

milk$logprice <- log(milk$price)
milk$logsales <- log(milk$sales)


milk_boot <- do(10000)*round((coef(lm(logsales ~ logprice, data = resample(milk)))[2]), 3)

confint(milk_boot, level = 0.95)
```




